\bf $\mathsf{TEDAT}$: Guaranteeing Bandwidth-based Availability for Services Over Inter-DC WAN

### 2021-01-16 paper.tex
add simulations

\begin{figure*}
\centering
\subfigure[Admission control]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/testbed-admit.pdf}}
\subfigure[Measured and demand ratio]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/testbed-public-2.pdf}}
\subfigure[Monetary gain after failures]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/test-bed-profit.pdf}}
\subfigure[Data loss ratio]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/testbed-data-loss-2.pdf}}
\caption{A public cloud example. Tenants' demands arrive obeying poisson process and the duration of demands are with exponential distribution.}
\label{e2}
\end{figure*}

@@

\caption{A private cloud example. We deploy three services whose details are shown in Table \ref{testbed-1}.}
\label{e1}
\end{figure*}

@@

Figure \ref{e2}(a) demonstrates $\mathsf{TEDAT}$ only performs slightly worse than the optimal solution (about 4\%) and is at least 2 $\times$ better than the \textit{Fixed} admission control.
This is because $\mathsf{TEDAT}$ fully considers the availability diversity of tenants.
In contrast, \textit{Fixed} admission control can't change tenants' routing during runtime and such inflexibility leads to higher rejection rate. 
Figure \ref{e2}(b) shows once a tenant's demand is admitted, $\mathsf{TEDAT}$ can guarantee bandwidth.
FFC and TEAVAR with \textit{Fixed} admission control perform slightly better than when they are without admission control since many tenants' demands are rejected, but they also perform worse than $\mathsf{TEDAT}$, because FFC is too conservative and and TEAVAR ignores the diverse demands.
Figure \ref{e2}(c) shows $\mathsf{TEDAT}$ can retain about 15\% more money ratio than FFC and TEAVAR when network fails.
This is because $\mathsf{TEDAT}$ pre-computes backup allocation with maximal profit and they can be put into practice as far as failures are detected.
Figure \ref{e2}(d) demonstrates data loss ratio after network fails, where $\mathsf{TEDAT}$ performs about 8\% worse than FFC.
FFC performs best since it keeps network utilization low and almost no congestion occurs when network fails, $\mathsf{TEDAT}$ can decrease performance loss by quick recovery.
%, where  FFC-1 and FFC-2 
%denote FFC with and without Fixed admission control,  respectively.
%where TEAVAR-1 and TEAVAR-2 are 
%denote TEAVAR with and without Fixed admission control, 
%We can see that 
%Specially, more than 85\% services achieve  95\% availability under $\mathsf{TEDAT}$, while only about 73\% and 60\%  services achieve this target under TEAVAR and FFC.
%Figure \ref{e2}(c) illustrates three schemes have similar performance for services with small availability target (i.e., $<95\%$).
%However, for services with large availability targets (i.e., $>=99\%)$,  $\mathsf{TEDAT}$ performs up to  20\% and 30\% better than TEAVAR and FFC.
%The reason for this is that $\mathsf{TEDAT}$ considers the diverse availability demands, so services with large targets can plunder
%bandwidth from others.
%Compared with TEAVAR, 20\% more applications satisfy their bandwidth demand with $\mathsf{TEDAT}$.
%Figure  \ref{e2}(c) shows the scheduled results with the same parameters.
%We can see the results approximate to that shown in Figure \ref{e2}(b).
%The gap is narrow, about 5\% on average.
%In the following evaluation, we develop a simulator to perform trace-driven simulations.
%Figure \ref{e2}(d) demonstrates the availability deviation between the testbed and simulation under the same parameters.
%We can see that the error is narrow, i.e., more than 90\% time the difference is less than 5\%.

@@

Figure \ref{e1}(a) shows the bandwidth-based availability which is measured as the time qualification ratio. A second is regarded as qualified if the gap between total measured bandwidth and bandwidth demand is less than 1\%.
We can see that all services can reach their availability targets under $\mathsf{TEDAT}$, while Service-1 fails under FFC and Service-2 fails under both TEAVAR and FFC.
To explore the reason, we show the scheduled results of the three schemes in TABLE \ref{testbed-1}:  
(1) FFC reserves too much bandwidth to protect routing and service1 is unable to gain enough bandwidth;
(2) $\mathsf{TEDAT}$ abandons link L4 for Service-2, while TEAVAR adopts it.
According to the link failure times shown in Figure \ref{e1}(b), we can see that most failures are from link L4 in our experiment.
Although TEAVAR considers link failure probability, it ignores the availability targets of different services.
Therefore, Service-3 gains redundant bandwidth and affects Service-2 finally.
%During L4 failure, service2 is unable to gain enough bandwidth. 
%and it will take much time for the controller to retrieve from congestion.
%All links are up under normal circumstances and the probability of this scenario is 98.9\%.
%We now consider a scenario in which DC4-DC5 link fails and other links are up.
%The probability of this failure scenario is about 1\%, which is about 10 $\times$ larger than the probability sum of other failure scenarios.
%We disable the link between DC4 and DC5 at $t=0.2s$ to produce this scenario.
%Figure \ref{e1}(c) shows aggregate bandwidth from DC1 to DC3.
%We can see SWAN drops about 33\% bandwidth between 0.2s and 1.1s.
%The result of service1 is similar.
Data loss mainly comes from congestion and blackhole, where congestion losses are always link oversubscribed and blackhole losses occur during the time between a link fails and ingress switch rescale.
Figure \ref{e1}(c) demonstrates $\mathsf{TEDAT}$-1 and FFC performs better than   $\mathsf{TEDAT}$-2  and TEAVAR for data losses ratio.
Data losses of Service-2 under TEAVAR is high due to Link L4.
Also, $\mathsf{TEDAT}$-2 ($\mathsf{TEDAT}$ without rescaling) performs worse than the other three schemes, because it takes much time to derive new resource allocation when network fails.
%We can see that $\mathsf{TEDAT}$-1 and FFC performs better than   $\mathsf{TEDAT}$-2  and TEAVAR.
%The losses of TEAVAR mainly comes from link $L4$ failure which is adopt by Service-2.
Figure \ref{e1}(d) shows the time of events after link L3 fails.
When L3 fails, DC1 and DC4 take about 0.4s to detect the failure.
$\mathsf{TEDAT}$-1 can  rescale traffic with the backup allocation results, therefore, packet losses will stop immediately.
%Control messages distributing and switch updating take about 0.3s, while the most time-consuming operation is TE computation which takes about 1s, 
%therefore, $\mathsf{TEDAT}$-2 performs relatively worse than other schemes.
%$\mathsf{TEDAT}$ considers link failure probability as well as the diverse demands of services \textit{proactively}, as a result, the time consuming events shown in Figure  \ref{e1}(c) rarely happens.

@@

\begin{figure*}[t]
\centering
%\begin{tabular}{c}
%\includegraphics[width=0.7\textwidth]{fig/evaluation/legend.pdf}
%\end{tabular}
%\vfill
\subfigure[IBM]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/admit.pdf}}
\subfigure[B4 ]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/att.pdf}}
\subfigure[ATT]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/cernet3.pdf}}
\subfigure[Cernet]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/cernet3.pdf}}
\caption{$\mathsf{TEDAT}$  vs. various TE schemes under different network topologies.}
\label{availability_fig1}
\end{figure*}
\begin{figure*} 
   \begin{minipage}[t]{0.25\linewidth} 
    \centering 
    \includegraphics[width=1.8 in]{fig/evaluation/link-utilization.pdf}
    \caption{Weight difference.} 
    \label{fig-weight} 
  \end{minipage}% 
   \begin{minipage}[t]{0.25\linewidth} 
    \centering 
    \includegraphics[width=1.8 in]{fig/evaluation/admission-control-time.pdf}
    \caption{Weight difference.} 
    \label{fig-weight} 
  \end{minipage}% 
%  \begin{minipage}[t]{0.24\linewidth} 
%    \centering 
%    \includegraphics[width=1.7 in]{fig/evaluation/weightnumber.pdf} 
%    \caption{Important profit.} 
%    \label{fig-weightnumber} 
%  \end{minipage}% 
   \begin{minipage}[t]{0.25\linewidth} 
    \centering 
    \includegraphics[width=1.8 in]{fig/evaluation/error.pdf}
    \caption{Weight difference.} 
    \label{fig-weight} 
  \end{minipage}% 
     \begin{minipage}[t]{0.25\linewidth} 
    \centering 
    \includegraphics[width=1.8 in]{fig/evaluation/optimization_time.pdf}
    \caption{Weight difference.} 
    \label{fig-weight} 
  \end{minipage}%

\end{figure*}

@@

FFC tries to maximize the link utilization with considering $l$ faults occur and we choose $l=1$ as its default value.

@@

%\begin{figure*}[t]
%\centering
%%\subfigure[Weight differentiation]{
%%\includegraphics[width=0.32\textwidth]{fig/evaluation/Geometric.pdf}}
%%\subfigure[Solution comparison]{
%%\includegraphics[width=0.32\textwidth]{fig/evaluation/version.pdf}}
%%\subfigure[Tunnel selection]{
%%\includegraphics[width=0.32\textwidth]{fig/evaluation/routing.pdf}}
%\subfigure[Profit comparison]{
%\includegraphics[width=0.32\textwidth]{fig/evaluation/fake/totalprofit.pdf}}
%\subfigure[Target satisfaction percentage]{
%\includegraphics[width=0.32\textwidth]{fig/evaluation/weight.pdf}}
%\subfigure[Availability comparison]{
%\includegraphics[width=0.32\textwidth]{fig/evaluation/fake/availability-cdf.pdf}}
%%\subfigure[Same importance]{
%%\includegraphics[width=0.24\textwidth]{fig/evaluation/sameweight.pdf}}
%\caption{Performance comparison under different metrics with IBM topology and traffic trace.}
%\label{motivatio_fig2}
%\end{figure*}

@@

\subsubsection{$\mathsf{TEDAT}$ vs. state-of-the-art TE schemes}\label{scales}
%From the comparison between the scheduled and testbed results, we can see that the scheduled results match the real testbed quite well,
%so in the following part, we will use trace-driven simulation to evaluate the performance of $\mathsf{TEDAT}$.

@@

Figure \ref{availability_fig1} shows the consistent trend under various topologies:
$\mathsf{TEDAT}$ performs about 20\%, 25\%, 30\%,  40\% better than TEAVAR, SMORE, SWAN, FFC, respectively.
%Specially, when traffic scale is 3, more than 70\% applications can satisfy their availability demands, which is at least 30\% better than TEAVAR.
Specially, the advantage of $\mathsf{TEDAT}$  is more obvious when there are resource competition (e.g., $s=3$).
%The reason for this is that $\mathsf{TEDAT}$ considers the bandwidth-based availability demand differentiation of applications.
This picture also demonstrates that the performance of $\mathsf{TEDAT}$ doesn't depend on particular network topology and traffic.
Next, we take IBM trace as the example and perform the experiments.

Figure \ref{motivatio_fig2}(a) shows total profit comparison between $\mathsf{TEDAT}$ and other schemes.
We can see that   $\mathsf{TEDAT}$ performs best and its performance is even up to 30\%, 40\%, 50\%, 75\% better than TEAVAR, SMORE, SWAN and FFC when traffic scale is 3.
Figure \ref{motivatio_fig2}(b) shows the percentage of services whose availability targets are satisfied for different importance levels when traffic scale is 3. 
In the picture, L, U, N, I, S are abbreviations of Lax, Unimportant, Normal, Important and Significant, and the error bar paints the mean
and mean $\pm$ standard deviation value.
We can see $\mathsf{TEDAT}$ performs even worse than other TE schemes for the Lax services, but it performs at least 25\% better for the Important and Significant services.
%We can see that  40\% more important services (i.e., Important, Significant) under $\mathsf{TEDAT}$ can meet their availability demands.
%,since the importance of services is taken into consideration under  $\mathsf{TEDAT}$, while most schemes ignore this.
Specially, we can see that SWAN \cite{swan} also performs well for the importance services, but it allocates bandwidth only in strict precedence across  three coarse priority classes and  $\mathsf{TEDAT}$ is  fine-grained priority and can describe the five level of importance.
 $\mathsf{TEDAT}$ aims to maximize the sum profit of all services, where a service's profit is defined in (\ref{availability}).
Figure \ref{motivatio_fig2}(c) presents the CDF of achieved availability for different schemes when traffic scale is 3.
We can see that about 87\%  services's achieved availability are larger than 95\% under  $\mathsf{TEDAT}$, which is at least 30\% better than other schemes.
%Figure \ref{motivatio_fig2}(a) shows that larger tunnel number can provide slighter higher availability.
%This is because that more alternative tunnels can be used to meet the bandwidth demands.
%Our trace doesn't contain application level traffic matrix, so we divide the original WAN traffic into $|J|=30$ parts randomly.
%Figure \ref{motivatio_fig2}(b) demonstrates the performance with more application division.
%We can see the performance is consistent for various application number.
%

@@

Solution error mainly comes from scenario pruning and greedy heuristic algorithm.

>>>>

\begin{figure*}
\centering
\subfigure[Admission control]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/testbed-admit.pdf}}
\subfigure[Measured and demand ratio]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/testbed-public-2.pdf}}
\subfigure[Monetary gain after failures]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/test-bed-profit.pdf}}
\subfigure[Data loss ratio]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/testbed-data-loss-2.pdf}}
\caption{A public cloud example: tenants' demands arrive obeying poisson process and the duration of demands are with exponential distribution.}
\label{e2}
\end{figure*}

@@

\caption{A private cloud example: we deploy three services whose details are shown in Table \ref{testbed-1}.}
\label{e1}
\end{figure*}

@@

Figure \ref{e2}(a) demonstrates $\mathsf{TEDAT}$ only performs slightly worse than the optimal solution (about 4\%) and is at least 2 $\times$ better than the \textit{Fixed} admission control.
This is because $\mathsf{TEDAT}$ fully considers the availability diversity of tenants.
In contrast, \textit{Fixed} admission control can't change tenants' routing during runtime and such inflexibility leads to higher rejection rate. 
Figure \ref{e2}(b) shows once a tenant's demand is admitted, $\mathsf{TEDAT}$ can guarantee bandwidth.
FFC and TEAVAR with \textit{Fixed} admission control perform slightly better than when they are without admission control since many tenants' demands are rejected, but they also perform worse than $\mathsf{TEDAT}$, because FFC is too conservative and and TEAVAR ignores the diverse demands.
Figure \ref{e2}(c) shows $\mathsf{TEDAT}$ can retain about 15\% more money ratio than FFC and TEAVAR when network fails.
This is because $\mathsf{TEDAT}$ pre-computes backup allocation with maximal profit and they can be put into practice as far as failures are detected.
Figure \ref{e2}(d) demonstrates data loss ratio after network fails, where $\mathsf{TEDAT}$ performs about 8\% worse than FFC.
FFC performs best since it keeps network utilization low and almost no congestion occurs when network fails, 
while $\mathsf{TEDAT}$ focuses on Monetary gain rather than data loss.
%, where  FFC-1 and FFC-2 
%denote FFC with and without Fixed admission control,  respectively.
%where TEAVAR-1 and TEAVAR-2 are 
%denote TEAVAR with and without Fixed admission control, 
%We can see that 
%Specially, more than 85\% services achieve  95\% availability under $\mathsf{TEDAT}$, while only about 73\% and 60\%  services achieve this target under TEAVAR and FFC.
%Figure \ref{e2}(c) illustrates three schemes have similar performance for services with small availability target (i.e., $<95\%$).
%However, for services with large availability targets (i.e., $>=99\%)$,  $\mathsf{TEDAT}$ performs up to  20\% and 30\% better than TEAVAR and FFC.
%The reason for this is that $\mathsf{TEDAT}$ considers the diverse availability demands, so services with large targets can plunder
%bandwidth from others.
%Compared with TEAVAR, 20\% more applications satisfy their bandwidth demand with $\mathsf{TEDAT}$.
%Figure  \ref{e2}(c) shows the scheduled results with the same parameters.
%We can see the results approximate to that shown in Figure \ref{e2}(b).
%The gap is narrow, about 5\% on average.
%In the following evaluation, we develop a simulator to perform trace-driven simulations.
%Figure \ref{e2}(d) demonstrates the availability deviation between the testbed and simulation under the same parameters.
%We can see that the error is narrow, i.e., more than 90\% time the difference is less than 5\%.

@@

Figure \ref{e1}(a) shows the bandwidth-based availability which is measured as the time qualification ratio. A second is regarded as qualified if the gap between total measured bandwidth and bandwidth demand is less than 1\%.
We can see that all services can reach their availability targets under $\mathsf{TEDAT}$, while Service-1 fails under FFC and Service-2 fails under both TEAVAR and FFC.
To explore the reason, we show the scheduled results of the three schemes in TABLE \ref{testbed-1}:  
(1) FFC reserves too much bandwidth to protect routing and service1 is unable to gain enough bandwidth;
(2) $\mathsf{TEDAT}$ abandons link L4 for Service-2, while TEAVAR adopts it.
According to the link failure times shown in Figure \ref{e1}(b), we can see that most failures are from link L4 in our experiment.
Although TEAVAR considers link failure probability, it ignores the availability targets of different services.
Therefore, Service-3 gains redundant bandwidth and affects Service-2 finally.
%During L4 failure, service2 is unable to gain enough bandwidth. 
%and it will take much time for the controller to retrieve from congestion.
%All links are up under normal circumstances and the probability of this scenario is 98.9\%.
%We now consider a scenario in which DC4-DC5 link fails and other links are up.
%The probability of this failure scenario is about 1\%, which is about 10 $\times$ larger than the probability sum of other failure scenarios.
%We disable the link between DC4 and DC5 at $t=0.2s$ to produce this scenario.
%Figure \ref{e1}(c) shows aggregate bandwidth from DC1 to DC3.
%We can see SWAN drops about 33\% bandwidth between 0.2s and 1.1s.
%The result of service1 is similar.
Data loss mainly comes from congestion and blackhole, where congestion losses are always link oversubscribed and blackhole losses occur during the time between a link fails and ingress switch rescale.
Figure \ref{e1}(c) demonstrates $\mathsf{TEDAT}$ and FFC performs better than   $\mathsf{TEDAT}$-WT  and TEAVAR for data losses ratio.
Data losses of Service-2 under TEAVAR is high due to Link L4 failings.
$\mathsf{TEDAT}$-WT performs worse than the other three schemes, because it takes much time to derive new resource allocation when network fails and the events time of  $\mathsf{TEDAT}$-WT shown in Figure \ref{e1}(d) just prove this.
%We can see that $\mathsf{TEDAT}$-1 and FFC performs better than   $\mathsf{TEDAT}$-2  and TEAVAR.
%The losses of TEAVAR mainly comes from link $L4$ failure which is adopt by Service-2.
%When L3 fails, DC1 and DC4 take about 0.4s to detect the failure.
%$\mathsf{TEDAT}$-1 can  rescale traffic with the backup allocation results, therefore, packet losses will stop immediately.
%Control messages distributing and switch updating take about 0.3s, while the most time-consuming operation is TE computation which takes about 1s, 
%therefore, $\mathsf{TEDAT}$-2 performs relatively worse than other schemes.
%$\mathsf{TEDAT}$ considers link failure probability as well as the diverse demands of services \textit{proactively}, as a result, the time consuming events shown in Figure  \ref{e1}(c) rarely happens.

@@

\begin{figure*}[t]
\centering
%\begin{tabular}{c}
%\includegraphics[width=0.7\textwidth]{fig/evaluation/legend.pdf}
%\end{tabular}
%\vfill
\subfigure[IBM]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/sim-admit.pdf}}
\subfigure[B4 ]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/att.pdf}}
\subfigure[ATT]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/cernet3.pdf}}
\subfigure[Cernet]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/cernet3.pdf}}
\caption{$\mathsf{TEDAT}$  vs. various TE schemes under different network topologies.}
\label{availability_fig1}
\end{figure*}

\begin{figure}
\centering
\subfigure[Admission control]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/link-utilization.pdf}}
\subfigure[Measured and demand ratio]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/admission-control-time.pdf}}
\caption{Benefits of admission control.}
\label{admission-benefit}
\end{figure}

%\begin{figure*} 
%   \begin{minipage}[t]{0.25\linewidth} 
%    \centering 
%    \includegraphics[width=1.8 in]{fig/evaluation/link-utilization.pdf}
%    \caption{Weight difference.} 
%    \label{fig-weight} 
%  \end{minipage}% 
%   \begin{minipage}[t]{0.25\linewidth} 
%    \centering 
%    \includegraphics[width=1.8 in]{fig/evaluation/admission-control-time.pdf}
%    \caption{Weight difference.} 
%    \label{fig-weight} 
%  \end{minipage}% 
%%  \begin{minipage}[t]{0.24\linewidth} 
%%    \centering 
%%    \includegraphics[width=1.7 in]{fig/evaluation/weightnumber.pdf} 
%%    \caption{Important profit.} 
%%    \label{fig-weightnumber} 
%%  \end{minipage}% 
%   \begin{minipage}[t]{0.25\linewidth} 
%    \centering 
%    \includegraphics[width=1.8 in]{fig/evaluation/error.pdf}
%    \caption{Weight difference.} 
%    \label{fig-weight} 
%  \end{minipage}% 
%     \begin{minipage}[t]{0.25\linewidth} 
%    \centering 
%    \includegraphics[width=1.8 in]{fig/evaluation/optimization_time.pdf}
%    \caption{Weight difference.} 
%    \label{fig-weight} 
%  \end{minipage}% 
%  
%\end{figure*}

@@

FFC tries to maximize the link utilization with considering 1 fault could occur in our evaluation.

@@

\begin{figure}
\centering
\subfigure[Admission control]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/error.pdf}}
\subfigure[Measured and demand ratio]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/optimization_time.pdf}}
\caption{Benefits of admission control.}
\label{admission-benefit}
\end{figure}
%\begin{figure*}[t]
%\centering
%%\subfigure[Weight differentiation]{
%%\includegraphics[width=0.32\textwidth]{fig/evaluation/Geometric.pdf}}
%%\subfigure[Solution comparison]{
%%\includegraphics[width=0.32\textwidth]{fig/evaluation/version.pdf}}
%%\subfigure[Tunnel selection]{
%%\includegraphics[width=0.32\textwidth]{fig/evaluation/routing.pdf}}
%\subfigure[Profit comparison]{
%\includegraphics[width=0.32\textwidth]{fig/evaluation/fake/totalprofit.pdf}}
%\subfigure[Target satisfaction percentage]{
%\includegraphics[width=0.32\textwidth]{fig/evaluation/weight.pdf}}
%\subfigure[Availability comparison]{
%\includegraphics[width=0.32\textwidth]{fig/evaluation/fake/availability-cdf.pdf}}
%%\subfigure[Same importance]{
%%\includegraphics[width=0.24\textwidth]{fig/evaluation/sameweight.pdf}}
%\caption{Performance comparison under different metrics with IBM topology and traffic trace.}
%\label{motivatio_fig2}
%\end{figure*}

@@

\subsubsection{Performance under real network topologies}\label{scales}
%From the comparison between the scheduled and testbed results, we can see that the scheduled results match the real testbed quite well,
%so in the following part, we will use trace-driven simulation to evaluate the performance of $\mathsf{TEDAT}$.

@@

Figure \ref{availability_fig1}(a)  shows $\mathsf{TEDAT}$ has only about 3\% performance gap from the optimal solution and can accept about 50\% more demands than the \textit{Fixed} consistently.
Similar to \cite{Teavar}, we next start a post-processing simulation, in which intends to send entirely bandwidth under each scenario at each time slot.
%We write down the bandwidth loss of each scenario for each demand and each scenario's corresponding probability.
The sum of scenario probability where demand is fully satisfied reflects the \textit{achieved availability}.
If a demand's achieved availability is higher than its availability target throughout duration time slots, then the availability defined in SLA is \textit{satisfication}.
Figure \ref{availability_fig1}(b) demonstrates that $\mathsf{TEDAT}$ can meet the availability SLAs of 40\% more demands than other traffic engineer algorithms.
The violation of SLA for $\mathsf{TEDAT}$ comes from demands rejection.
The reason for this is that $\mathsf{TEDAT}$ adopts admission control and it considers the diverse availability targets of different bandwidth demands.
$\mathsf{TEDAT}$ can make demands with stringent availability requirements pass links with high reliability, therefore, their availability targets can be guaranteed, but other schemes are unable differentiate demands.
To show this benefit, we adopt \textit{Fixed} admission control for each traffic scheduling algorithm and Figure \ref{availability_fig1}(c) shows the comparisons.
We can see that $\mathsf{TEDAT}$ performs at least 10\% better than other algorithms even under the same admission method.
%Satisfaction percentage. It denotes the percentages of applications whose achieved availability is larger than the corresponding target.
%Figure \ref{availability_fig1}(b) shows 
%$\mathsf{TEDAT}$ performs about 20\%, 25\%, 30\%,  40\% better than TEAVAR, SMORE, SWAN, FFC, respectively.
%%Specially, when traffic scale is 3, more than 70\% applications can satisfy their availability demands, which is at least 30\% better than TEAVAR.
%Specially, the advantage of $\mathsf{TEDAT}$  is more obvious when there are resource competition (e.g., $s=3$).
%%The reason for this is that $\mathsf{TEDAT}$ considers the bandwidth-based availability demand differentiation of applications.
%This picture also demonstrates that the performance of $\mathsf{TEDAT}$ doesn't depend on particular network topology and traffic.
%Next, we take IBM trace as the example and perform the experiments.

%Figure \ref{motivatio_fig2}(a) shows total profit comparison between $\mathsf{TEDAT}$ and other schemes.
%We can see that   $\mathsf{TEDAT}$ performs best and its performance is even up to 30\%, 40\%, 50\%, 75\% better than TEAVAR, SMORE, SWAN and FFC when traffic scale is 3.
%Figure \ref{motivatio_fig2}(b) shows the percentage of services whose availability targets are satisfied for different importance levels when traffic scale is 3. 
%In the picture, L, U, N, I, S are abbreviations of Lax, Unimportant, Normal, Important and Significant, and the error bar paints the mean
%and mean $\pm$ standard deviation value.
%We can see $\mathsf{TEDAT}$ performs even worse than other TE schemes for the Lax services, but it performs at least 25\% better for the Important and Significant services.
%%We can see that  40\% more important services (i.e., Important, Significant) under $\mathsf{TEDAT}$ can meet their availability demands.
%%,since the importance of services is taken into consideration under  $\mathsf{TEDAT}$, while most schemes ignore this.
%Specially, we can see that SWAN \cite{swan} also performs well for the importance services, but it allocates bandwidth only in strict precedence across  three coarse priority classes and  $\mathsf{TEDAT}$ is  fine-grained priority and can describe the five level of importance.
% $\mathsf{TEDAT}$ aims to maximize the sum profit of all services, where a service's profit is defined in (\ref{availability}).
%Figure \ref{motivatio_fig2}(c) presents the CDF of achieved availability for different schemes when traffic scale is 3.
%We can see that about 87\%  services's achieved availability are larger than 95\% under  $\mathsf{TEDAT}$, which is at least 30\% better than other schemes.
%Figure \ref{motivatio_fig2}(a) shows that larger tunnel number can provide slighter higher availability.
%This is because that more alternative tunnels can be used to meet the bandwidth demands.
%Our trace doesn't contain application level traffic matrix, so we divide the original WAN traffic into $|J|=30$ parts randomly.
%Figure \ref{motivatio_fig2}(b) demonstrates the performance with more application division.
%We can see the performance is consistent for various application number.
%

@@

%Solution error mainly comes from scenario pruning and greedy heuristic algorithm.
